
\documentclass{article}
\usepackage{url}
\setlength\parindent{0pt}
\title{Red Lobster Cheddar Bay Biscuits (copy cat)}

\begin{document}
\maketitle
{\small
\textit{Notes: This recipe is from Damn Delicious at \url{http://damndelicious.net/2014/02/03/red-lobster-cheddar-bay-biscuits/}}}
\\\\

Time: 20 minutes

Materials: oven, cookie sheet, microwaveable bowl, mixing bowl, basting brush

\section{Ingredients}

\textit{Makes 10 large biscuits}

2 cups all-purpose flour

1 Tbsp. sugar

1 Tbsp. baking powder

2 tsp. garlic powder

$1/2$ tsp. sea salt or kosher salt

$1/4$ tsp. cayenne pepper (optional)

1 cup buttermilk or 1 cup whole milk with a quarter of a lemon juiced in

$1/2$ cup unsalted butter, melted

1 $1/2$ cup shredded sharp cheddar cheese
\\
\\
\textbf{For the Topping}

3 Tbsp. unsalted butter, melted

1 Tbsp. chopped fresh parsley leaves

$1/2$ tsp. garlic powder

\section{Recipe}
\begin{enumerate}
\item{Pre-heat oven to $450^{\circ}$ F. Line a cookie sheet with parchment paper or a silicone baking mat.}
\item{In a large bowl, combine flour, sugar, baking powder, garlic powder, salt and cayenne pepper, if using.}
\item{In a large glass measuring cup or another bowl, whisk together buttermilk and butter. Pour mixture over dry ingredients and stir using a rubber spatula just until moist. Gently fold in cheese.}
\item{Using a $1/4$-cup measuring cup, scoop the batter evenly onto the prepared baking sheet. Place into oven and bake for 10-12 minutes, or until golden brown.}
\item{For the topping, whisk together butter, parsley and garlic powder in a small bowl. Working one at a time, brush the tops of the biscuits with the butter mixture.}
\item{Serve immediately.}
\end{enumerate}
\end{document}
